Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-09 outputs/paper/paper.qmd
Update paper.qmd

## Methodology
The data for the trend in US Birth Rates, births per 1,000 women age 15-44 from the period 1980 to 2020 was acquired from CDC Vital Statistics Births Reports for 2015, 2019 and 2020 (Martin and Mathews 2017; Martin and Driscoll 2021; Hamilton and Osterman 2021). Another trends in Birth Rates by Population Subgroup, specifically birth rates by age group, race and ethnicity are again gathered from CDC Vital Statistics Births Reports. Original paper uses single-age population counts, among all races from 1969-2019 and by race and Hispanic origin from 1990-2019, from the CDC SEER database (CDC NCI 2021).

@@

Figure 3 B, major religion of Hispanic, Black, White  religious reason of each race and ethnicity

>>>>

## Methodology
The data for the trend in US Birth Rates, births per 1,000 women age 15-44 from the period 1980 to 2020 was acquired from CDC Vital Statistics Births Reports for 2015, 2019 and 2020 (Martin and Mathews 2017; Martin and Driscoll 2021; Hamilton and Osterman 2021). Another trends in Birth Rates by Population Subgroup, specifically birth rates by age group, race and ethnicity are again gathered from CDC Vital Statistics Births Reports. Original paper uses single-age population counts, among all races from 1969-2019 and by race and Hispanic origin from 1990-2019, from the CDC SEER database (CDC NCI 2021). Data is available freely at https://seer.cancer.gov/popdata/download.html and raw files can be found in the data/pop/folder of the original replication package.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| label: tbl-race-table
#| tbl-cap: "Race and ethinicity (ages 15-44)"

#### Table 1a ####
# Count the number of births per 1,000 women in relevant population subgroup by their race and ethinicity in the ages cohort from 15 to 44. 
#### ####

# Install the necessary packages if not already installed
install.packages(c("knitr","lubridate","tidyverse","kableExtra"))

# Load required libraries
library(dplyr)
library(knitr)
library(lubridate)
library(tidyverse)
library(kableExtra)

# Load the CSV file

```
Figure 3 B, major religion of Hispanic, Black, White  religious reason of each race and ethnicity
